R Notebook

### 2021-09-13 documentation_and_analysis/draftbook.Rmd
rbind of no2 data

```{r}
# Reading in and skipping first 5 rows
uk_ev <- read_ods(here("raw_data/ev_by_la.ods"), skip = 5)
# Making row 1 the variable name
names(uk_ev) <- uk_ev[1,] 
# Removing row 1 
uk_ev <- uk_ev[-1,] %>% 
  clean_names()
```

@@

```{r}
# Joining uk_ev + shape file 
uk_ev_map <- uk_ev %>% 
  left_join(uk_shape_file, by = c("ons_la_code_apr_2019" = "lad19cd")) %>% 
  drop_na() %>% 
  mutate(across(c(x2021_q1:x2011_q4), as.numeric))
```

```{r}
    pal <- colorBin("Greens", domain = uk_ev_map$x2021_q1, bins = 10)

    uk_ev_map_labels <- sprintf(
      uk_ev_map$region_local_authority_apr_2019_3, uk_ev_map$x2021_q1)
```

```{r}
leaflet(uk_ev_map) %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(data = uk_ev_map$geometry,
             # fillColor = ~pal(x2021_q1),
              weight = 0.5,
              opacity = 0.9, 
              color = "green",
              fillOpacity = 0,
              highlightOptions = highlightOptions(color = "white", weight = 2,
                                                      bringToFront = TRUE),
              label = uk_ev_map_labels,
                  labelOptions = labelOptions(
                    style = list("font-weight" = "normal", padding = "3px 8px"),
                    textsize = "15px",
                    direction = "auto")) %>% 
  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
                position = "bottomright")
```

```{r}
uk_ev_map$x2021_q1 %>% 
  range()
```

>>>>

```{r}
# Reading in and skipping first 5 rows
uk_ev <- read_ods(here("raw_data/ev_by_la.ods"), sheet = 2, skip = 5)
# Making row 1 the variable name
names(uk_ev) <- uk_ev[1,] 
# Removing row 1 
uk_ev <- uk_ev[-1,] %>% 
  clean_names()
```

@@

```{r}
# Joining uk_ev + shape file 
uk_ev_map <- uk_ev %>% 
  left_join(uk_shape_file, by = c("ons_la_code_apr_2019" = "lad19cd")) %>% 
  drop_na() %>% 
  mutate(across(c(x2021_q1:x2011_q4), as.numeric)) %>% 
  st_as_sf()
```

```{r}
    pal <- colorBin("Greens", domain = uk_ev_map$x2021_q1, bins = c(0, 500, 1000, 2500, 5000, 10000, 15000))

    uk_ev_map_labels <- sprintf(
      "<strong>%s</strong><br/>%g Electric Vehicles",
      uk_ev_map$region_local_authority_apr_2019_3, uk_ev_map$x2021_q1) %>% 
      lapply(htmltools::HTML)
```

```{r}
uk_ev_map %>% 
  leaflet() %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~pal(x2021_q1),
    weight = 0.1,
    opacity = 0.9, 
    color = "black",
    fillOpacity = 0.8,
    highlightOptions = highlightOptions(color = "green", weight = 2,
                                        bringToFront = TRUE),
    label = uk_ev_map_labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>% 
  addLegend(pal = pal, values = ~x2021_q1, opacity = 0.7, title = NULL,
            position = "bottomright")
```
